---
title: |
  <i class="nes-icon coin is-large"></i>
  NES Theme
  <i class="nes-icon coin is-large"></i>
subtitle: "for Quarto revealjs"
author: "Emil Hvitfeldt"
format: nes-revealjs
---

# Header 1

## Header 2

### Header 3

Normal text

**Bold text**

*italics*

~~strikethrough~~

[links](https://www.xaringan.gallery/).

## Code expressions

Code chunks and output

```{r}
#| echo: true
lm(mpg ~ disp, data = mtcars)
```

## Block quotes

> Dorothy followed her through many of the beautiful rooms in her
> castle.

## Ordered list

1.  First item
2.  Second item
3.  Third item
    1.  Indented item
    2.  Indented item
4.  Fourth item

## Unordered list

-   First item
-   Second item
-   Third item
-   Fourth item

## ggplot2

```{r scatter}
#| echo: true
#| warning: false
#| output-location: slide
library(palmerpenguins)
library(showtext)
library(ggplot2)
font_add_google("Press Start 2P")
showtext_auto()

colors <- c("#76c442", "#f2c409", "#ce372b")

ggplot(penguins) +
  aes(bill_length_mm, bill_depth_mm,
      color = species) +
  geom_point() +
  theme_minimal(base_family = "Press Start 2P") +
  scale_color_manual(values = colors)
```

You can avoid showtext by having [Press Start
2P](https://fonts.google.com/specimen/Press+Start+2P) font installed

## Social Media Icons

Many different icons

<i class="nes-icon twitter is-large"></i>
<i class="nes-icon facebook is-large"></i>
<i class="nes-icon instagram is-large"></i>
<i class="nes-icon github is-large"></i>
<i class="nes-icon google is-large"></i>
<i class="nes-icon gmail is-large"></i>
<i class="nes-icon medium is-large"></i>
<i class="nes-icon linkedin is-large"></i>
<i class="nes-icon twitch is-large"></i>
<i class="nes-icon youtube is-large"></i>
<i class="nes-icon reddit is-large"></i>
<i class="nes-icon whatsapp is-large"></i>

<br>

<br>

### In different sizes

::: columns
::: {.column width="33%"}
"is-small"

<i class="nes-icon twitter is-small"></i>
:::

::: {.column width="33%"}
"is-medium"

<i class="nes-icon twitter is-medium"></i>
:::

::: {.column width="33%"}
"is-large"

<i class="nes-icon twitter is-large"></i>
:::
:::

## Reaction Icons

<i class="nes-icon is-large heart"></i>
<i class="nes-icon is-large is-half heart"></i>
<i class="nes-icon is-large is-transparent heart"></i>
<i class="nes-icon is-large heart is-empty"></i>

<i class="nes-icon is-large star"></i>
<i class="nes-icon is-large star is-half"></i>
<i class="nes-icon is-large star is-transparent"></i>
<i class="nes-icon is-large star is-empty"></i>

<i class="nes-icon is-large like"></i>
<i class="nes-icon is-large like is-empty"></i>

<br>

### And more

<i class="nes-icon close is-large"></i>
<i class="nes-icon trophy is-large"></i>
<i class="nes-icon coin is-large"></i>
